\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2020-11-20 submission/manuscript.tex
References customization.
Formatting text.
Unit format rendering.

Proteins were isolated according to the protocol for protein isolation
from soil described in Chourey \emph{et al.} (2010) and modified by
Hultman \emph{et al.} (2015). This protocol was further modified and
adapted for microbial protein isolation from macrophyte surfaces as
described below. Twenty (20) \si{\ml} of protein extraction buffer (4
\si{\percent} SDS, 100 \si{\milli\Molar} Tris-HCl {[}pH 8.0{]}) was
added to 5 \si{\g} wet weight of leaves or 10 \si{\g} wet weight of
thalli. The mixture was incubated in boiling water for 5 \si{\minute},
vortexed for 10 \si{\minute} and incubated again in boiling water for 5
\si{\minute}. After a brief vortex, the lysate was transferred to a
clean tube separating the host leaves or thalli from the mixture
containing lysed epiphytic cells. Dithiothreitol (DTT; final
concentration 24 \si{\milli\Molar}) was added and proteins were
precipitated with chilled 100 \si{\percent} trichloroacetic acid (TCA;
final concentration 20 \si{\percent}) overnight at \num{-20} °C.
Precipitated proteins were centrifuged at 10,000 × g and 4
\si{\degreeCelsius} for 40 \si{\minute}. The obtained protein pellet was
washed three times with chilled acetone. During the first washing step
the pellet was transferred to a clean 1.5 \si{\ml} tube. After each
washing step, samples were centrifuged at 20,000 × g and 4
\si{\degreeCelsius} for 5 \si{\minute}. Dried pellets were stored at
\num{-80} °C until further analysis.

@@

@@

\hypertarget{figure-captions}{%
\subsection{Figure Captions}\label{figure-captions}}

>>>>

Proteins were isolated according to the protocol for protein isolation
from soil described in Chourey \emph{et al.} (2010) and modified by
Hultman \emph{et al.} (2015). This protocol was further modified and
adapted for microbial protein isolation from macrophyte surfaces as
described below. Twenty (20) \si{\ml} of protein extraction buffer (4
\si{\percent} SDS, 100 \si{\milli\Molar} Tris-HCl {[}pH 8.0{]}) was
added to 5 \si{\g} wet weight of leaves or 10 \si{\g} wet weight of
thalli. The mixture was incubated in boiling water for 5 \si{\minute},
vortexed for 10 \si{\minute} and incubated again in boiling water for 5
\si{\minute}. After a brief vortex, the lysate was transferred to a
clean tube separating the host leaves or thalli from the mixture
containing lysed epiphytic cells. Dithiothreitol (DTT; final
concentration 24 \si{\milli\Molar}) was added and proteins were
precipitated with chilled 100 \si{\percent} trichloroacetic acid (TCA;
final concentration 20 \si{\percent}) overnight at \num{-20}
\si{\degreeCelsius}. Precipitated proteins were centrifuged at 10,000 ×
g and 4 \si{\degreeCelsius} for 40 \si{\minute}. The obtained protein
pellet was washed three times with chilled acetone. During the first
washing step the pellet was transferred to a clean 1.5 \si{\ml} tube.
After each washing step, samples were centrifuged at 20,000 × g and 4
\si{\degreeCelsius} for 5 \si{\minute}. Dried pellets were stored at
\num{-80} \si{\degreeCelsius} until further analysis.

@@

\interlinepenalty=10000 \setlength{\emergencystretch}{3.5em}

@@

\hypertarget{figure-captions}{%
\subsection{Figure captions}\label{figure-captions}}
